\documentclass[article]{twentysecondcv_v2} % a4paper for A4

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}
\usepackage{xunicode}
\usepackage{fontawesome5}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\begin{document}

\begin{textblock}{20}(0.5,1.0)
\Large{\color{black}{Irfan Mohammad Al Hasib}\vspace{3pt}}\\
\medium{\color{gray}{Artificial Intelligence | Computer Vision Researcher}\vspace{5pt}}\\
\small{\color{mainblue}\faGlobeAsia\hspace{3pt}}{\href{https://irfanhasib0.github.io/}{\color{blue}https://irfanhasib0.github.io/}}\\
\small{\color{mainblue}\faAt\hspace{3pt}}{\color{blue}{irfanhasib.me@gmail.com}} \\
\small{\color{mainblue}\faPhone}{\color{black}{ +81 070 3832 6371}} \\
\end{textblock}

\begin{textblock}{15}(11,2.5)
\small{\color{mainblue}\faBlog}{ \href{https://irfanhasib0.github.io/blogs}{\color{blue}https://irfanhasib0.github.io/blogs}}\\
\iconurlnt{\color{mainblue}\faGoogle}{\https://scholar.google.com/citations?user=R5y_Ya8AAAAJ&hl=en}{Google Scholar Profile}\\
%\small{\color{mainblue}\faLinkedin}{ \href{https://www.linkedin.com/in/irfanhasib/}{\color{black}www.linkedin.com/in/irfanhasib/}}\\
\small{\color{mainblue}\faEnvelope}{\color{black}{ 6-1-5-206 Mayebaranishi, Funabashi, Chiba, Japan}} \\
\end{textblock}

\begin{textblock}{20}(0.5,4.0)
\heading{Summary}
Over the past five years, I have successfully developed many AI solutions for leading companies in Japan. I have am continuously exploring new research ideas, successfully published one recently, few more on progress. Moreover, my self-initiated projects and blogs would reflect my passion and proactive engagement with cutting-edge developments in the field.
\end{textblock}

\begin{textblock}{10}(0.5,6.5)
\section{Experience}
\Job{Vision AI Research Engineer}
{Digital Media Professionals Inc., Tokyo, Japan}
{February, 2024- Till Present}
{https://www.dmprof.com}
\begin{multiline}
>> Research and development of \textbf{object detection, semantic segmentation} and \textbf{6D object pose estimation} methods for precise pick and place operation.\\
>> Collaborating with the research work on \textbf{Vision Language Model} development for safe driving.
\end{multiline}\\

\Job{Computer Vision Engineer}
{Japan Infra Waymark (NTT West Group), Tokyo}
{August, 2021 - February, 2024}
{https://www.jiw.co.jp}
\begin{multiline}
>>  Development of metal and concrete structure defect/anomaly detection system from arial videos. Several top telecom and transportation companies in Japan used these solution.\\
%Worked with \textbf{Faster R-CNN , DeepLab, SPADE, NetVLAD } and many other SOTA algorithms \\ %\href{https://irfanhasib0.github.io/\#ai_project_link_2}{\itshape \color{blue} detail link}\\
%>> Led multiple client AI  projects from requirement analysis to deployment. \\
>> Development and maintenance of the \textbf{Machine Learning Pipeline} for production environment. %Frequently work with \textbf{Python, AWS, CI/CD , Linux systems, Docker} etc.
%\href  {https://irfanhasib0.github.io/\#ai_project_link_2}{\itshape \color{blue} detail link}\\
\end{multiline}\\

%%%-----------------------------

\Job{Artificial Intelligence Engineer}
{Hiperdyne Corporation, Japan }
{July, 2019- August 2021 }
{https://www.hiperdyne.com}
\begin{multiline}
>> Prediction of optimal control parameters for an industrial process with \textbf{Reinforcement Learning}\\ 
>> Shipment route optimization utilizing \textbf{AI based optimization techniques}. \\
%>> Development of \textbf{Deep Learning based system for Production KPI estimation}, from real time \textbf{sensor data} in a industry. \\
>> A system for \textbf{Production dynamics visualization using Machine Learning.}  \href  {https://irfanhasib0.github.io/\#ai_project_link_1}{\itshape \color{blue} visit here for more details}\\
\end{multiline}\\
({\color{gray} November, 2018- April, 2019} {AI and Language training.})\\


\Job{Jr. Research Engineer}
{Pi Labs Bangladesh Ltd. }
{August, 2017- September, 2018}
{www.pilabsbd.com}
\begin{multiline}
>> {IoT based} Room Monitoring System Development.\\
>>  Firmware development of a Programmable Fluid Pump.\\
>>  Package \textbf{tracking system} development \\
>>  Digital weight measuring device development for production line. \href{https://irfanhasib0.github.io/\#pi_project_link_4}{\itshape \color{blue} visit here for details}
\end{multiline}\\

\section{Co-Curricular Activities}
\begin{twentyshort}
\faBookmark[regular] Founding President at BUET Robotics Society} \iconurl{\faGlobeAsia}{https://www.facebook.com/groups/BUETRS/about}{(BRS)}{2016}\\
\faBookmark[regular] Co-organized Annual Robotics Competition for BRS \faClock[regular]{2016}
\end{twentyshort}
\end{textblock}

\begin{textblock}{9}(11.5,6.5)
\section{Education}
\begin{multiline} % Environment for a list with descriptions
\faBookmark[reguar] \textbf{\color{mainblue} B.Sc. in Mechanical Engineering}\\   \faMapMarker* \textbf{Bangladesh University of Engineering and Technology (BUET)} 
{\textbf{CGPA}: \textbf{3.23} out of 4.00} \faClock[regular] {2017}\\
\faBookmark[regular] {\textbf{IELTS} : Overall score \textbf{7.0}} \faClock[regular] {2024}\\
\faBookmark[regular] \textbf{ Higher Secondary School} {\emph{ GPA: 5.00 out of 5.00} \faClock[regular]{2011}\\
%\faBookmark[regular] \textbf{Secondary School} {\emph{ GPA: 5.00 out of 5.00} \faClock[regular] {2009}\\
%>> [2019]{ Language} { Japanese : Passed NAT-N5}
\end{multiline}\\

\section{Publications (lead author)}
\begin{multiline}
\faBookmark[regular] \textbf{Boosting auxiliary task guidance: a probabilistic approach}. Published in IAES International Journal of Artificial Intelligence,  \href{https://ijai.iaescore.com/index.php/IJAI/article/view/21444}{\itshape \color{blue} Volume 12, }\href{https://ijai.iaescore.com/index.php/IJAI/article/view/21444/13532}{\itshape \color{blue} PDF} \faClock[regular] {2023}\\
\faBookmark[regular] \textbf{Grad Queue : A probabilistic framework to reinforce sparse gradients}. \iconurl{}{https://arxiv.org/pdf/2404.16917}{pre-print}{2024}
\end{multiline}\\

\section{Achievements}
\begin{multiline}
\faBookmark[regular] Participated along with my team, Interplaneter in \href{http://urc.marssociety.org/}{\color{blue}University Rover challenge }. Our team attained \href{http://urc.marssociety.org/home/about-urc/urc2016-scores}{\color{blue}5th position} in Phobos final. I was in charge of \textbf{Robotic Manipulator Design and deployment}. The Competition is organized by  \href{https://www.marssociety.org/}{\color{blue}Mars Society} (USA) annually for college students world wide.
\iconurl{\faYoutube}{https://www.youtube.com/watch?v=MlN-VFj14LE}{watch video}{2016}
%https://youtu.be/f22zghezsQs?t=147
\faMapMarker*\hspace{3pt} {Utah, USA}
\end{multiline}\\

\section{Machine Learning Project}
\begin{multiline} % Environment for a short list with no descriptions
\faBookmark[regular] Vision AI blogs covering [i] Detection and Segmentation model families [ii] Evaluation of CNN \& \textbf{Transformer/ViT} architectures. \iconurl{\faBlog}{https://irfanhasib0.github.io/}{visit blogs}{2023}

\faBookmark[regular] Recent projects related to \textbf{Human Pose Tracking} models, Transformer, \textbf{Yolo-V8, DeepLab-V3, Diffusion Models} can be found here \iconurl{\faGithub}{https://irfanhasib0.github.io/blogs/}{github}{2023}\\
\faBookmark[regular] Implementation from scratch - [i] Fundamental ML algorithms - \textbf{ANN, SVM, KNN, Naive Bias} etc. [ii] RL Algorithms e.g. \textbf{DQN, DDPG, PPO} etc. [iii] Kaggle Challenge focusing on \textbf{Data preprocessing} methods and \textbf{hyperparameter tuning} techniques. \iconurl{\faGlobeAsia}{https://irfanhasib0.github.io/}{project page}{2020}
\end{multiline}\\

\section{Publications(co-author)}
\faBookmark[regular] Development of a two wheeled self balancing robot with speech recognition and navigation algorithm, \iconurl{\faGlobeAsia}{https://aip.scitation.org/doi/abs/10.1063/1.4958446}{AIP}{2016}\\
\faBookmark[regular] Integrating data mining and microsimulation modelling to reduce traffic congestion. \iconurl{\faGlobeAsia}{https://www.mdpi.com/2413-8851/3/2/41}{Journal : Urban Science}{2019}\\
\end{textblock}

\strut\newpage
\begin{textblock}{10}(0.5,0.5)

\section{Academic Project}\\
\faBookmark[regular] A Remote control Surveillance robot.The robot was able to pick up small objects from hole. It could also send temperature, pressure and video feed from an remote place using Bluetooth signal for surveillance support.\iconurl{}{https://irfanhasib0.github.io/\#buet_project_link}{(link)}{2015}\\
\faBookmark[regular] For undergrad thesis we  developed a precision velocity measurement system. We used Kalman filtering for \textbf{Sensor Fusion} and combined \textbf{GPS (Ublox-NEO 6) and IMU Sensor(MPU6050)} data. \iconurl{}{https://irfanhasib0.github.io/\#buet_project_link}{(link)}{2016}
\end{textblock}

\begin{textblock}{9}(11.5,0.5)
\section{Robotics Project}
\begin{multiline}
\faBookmark[regular] Optimal steering angle estimator \textbf{Model Predictive Controller (MPC)} and Iterative Linear Quadratic Regulator (ILQR) algorithms from scratch. \iconurl{\faGlobeAsia}{https://irfanhasib0.github.io/\#ilqr_mpc_link}{project page}{2019}\\
\faBookmark[regular] A simple two link Robot using \textbf{ROS and Gazebo}. \iconurl{\faYoutube}{https://www.youtube.com/watch?v=lJbyy89X7gM&ab_channel=IrfanHasib}{watch demo}{2018}\\
\faBookmark[regular] Small scale \textbf{Desktop CNC Machine} using  AVR Platform. \iconurl{\faGlobeAsia}{https://youtu.be/xU7YMPpZMYs?list=TLPQMTAwMzIwMjGHI57V0cC9IA}{watch demo}{2017}\\
\faBookmark[regular] Visually instructed \textbf{Robotic arm on AVR Platform}. \iconurlnt{\faYoutube}{https://www.youtube.com/watch?v=eevrzHHSlP4youtube}{watch demo} I also built a GUI software in python for controlling. \iconurl{\faYoutube}{https://www.youtube.com/watch?v=hj1Wc6-8-7w}{watch demo}{2014}
\end{multiline}
\end{textblock}
\end{document} 

\section{\large Deep Learning}\subsection{\small \textbf {Deep Neural Network, CNN}\newline \textbf{Transformers, Diffusion Models, LLMs} \newline \textbf{Reinforcement Learning} \newline Proficient in \textbf{TensorFlow , PyTorch, Keras}
\newline Proficient in 
\textbf{Python, Numpy, Pandas, Sklearn}}

\section{\large Machine Learning} \subsection{\small  
\textbf{Regression, SVM,Naive Bias, k-NN, Decision Tree, CART, Random Forest, AdaBoost, GBoosting, XGboost, Bagging, Boosting, Stacking, Ensemble, K Means Clustering }etc.}
\section{\large Computer Vision}\subsection{\small \textbf {CNN : YOLO, SSD, U-Net, DeepLab, R-CNN, ResNet, MobileNet, EfficientNet. CV : HOG, Haar, SURF, SIFT, ORB, 0pt. Flow, Segmentation, Detection, Tracking} etc.}
\section{\large Reinforcement Learning}\subsection{\small \textbf{Value Iteration, Policy Gradient, MDP, TD/MC Learning, DQN, DDPG, PPO, A2C, A3C
} etc. }
%}

%\makeprofile % Print the sidebar

%\newpage
%\cvnpage{
\section{\large Programming}
\subsection{\small \textbf{Python : Advanced Level (4 year +) \newline C++ : Intermediate Level (1.5 year)}
\newline Web Development, React JS : Basic (few months)}
\section{\large Data Analysis:}\subsection{\small \textbf{Standard Data Preprocessing Pipeline, SMOTE, Correlation \& Feature Importance Analysis, Confusion Matrix, AUC \& ROC, Data Visualization Tools, VAE, PCA, t-SNE, SVD, FFT, Wavelet Transform }etc.}
\section{\large Development Platform} \subsection{\small \textbf{Linux} : Intermediate Level (2 year +) \newline \textbf{GitHub} : Intermediate Level (3 year +) \newline \textbf{DBMS} (SQL) : Developing ( 1 year)  
\newline \textbf{Docker} : Developing ( 1 Year )
\newline \textbf{AWS} : EC2, S3, ECS, Lambda Developing ( 1 Year)  
\newline \textbf{Web Development} : Flask, Django (6 months)
\newline Spark \& Hadoop : Basic (Roughly a month)
\newline Kubernetes : (Learning)}
\section{\large Embedded System \& IoT } \subsection{\small
\textbf{AVR Micro-controller (C++)}, Basic ARM \newline ESP 8266, Raspberry Pi (Python, C++)}
\section{\large Engineering Mathematics:}\subsection{\small Linear Algebra, Vector \& Matrix, Transformations, Eigen-decomposition, Differential Calculus, Engineering Mathematics}

\section{\large Probability and Statistics :}\subsection{\small Data Distributions, Bayes Theorem, Entropy, Cross Entropy, KL-divergence, Information Gain , Relevant theorems of Probability, Statistics and Information Theory.}

\section{\large Robotics:}\subsection{\small  
\textbf{IoT \& Embedded System Design} 
\newline Path Planning Algorithms 
\newline Robot Vision Algorithms 
\newline Robot Operating System \textbf{(ROS)}
\newline \textbf{Visual Odometry and SLAM}}

\section{\large Data Structure and Algorithms  }\subsection {\small Data Structures and Sorting Algorithms \newline Graph and Tree based Algorithms \newline Recursion \& Dynamic Programming }

\section{\large Project Management} \subsection{\small Agile Project Management \newline Requirement Analysis \newline PM Tools : Trello, Asana}

}









